### 2019-05-14 tables/03_model_summary.Rmd
create model summary table

# setwd("tables")
# ---- cdl_key ----
cdl_key <- read.csv("../data/cdl/cdl_key.csv", stringsAsFactors = FALSE)
cdl_key %>%
  group_by(category) %>%
  sample_n(1) %>%
  knitr::kable(digits = 0, format = "markdown", caption = "Example of CDL categorizations.")

# ---- cdl summary ----
cdl_data <- read.csv("../data/cdl/cdl_summary.csv", stringsAsFactors = FALSE)

apply(cdl_data, 2, function(x) quantile(x, c(0.05, 0.5, 0.95), 
                                        na.rm = TRUE)) %>%
  data.frame() %>%
  dplyr::select(-llid) %>%
  t() %>%
  knitr::kable(format = "markdown", caption = "CDL summary statistics")
```

>>>>

# setwd("tables")
read.csv("../data/mcmc/model_r2.csv", 
                     stringsAsFactors = FALSE) %>%
  knitr::kable(digits = 2, format = "markdown", caption = "Model R2")
```
